How to compute the fusion product of MV cycles in type $A$

### 2021-05-27 draft.tex
63 begun

To prove this we require the following resutl from \cite{dthesis}.
\begin{theorem}
    \label{pr:govsasirrecs}
    The irreducible components of $\overline{\OO}^\lambda\cap\TT_\mu\cap\n$ are $\{{X(\tau)} : \tau\in YT(\lambda)_\mu\}$. 
\end{theorem}
% 
\begin{proof}[Proof of~\Cref{cor:iota}]
Since $\mathring X(\tau',\tau'')_{0,0}\subset\overline{\OO}^\lambda\cap\TT_\mu\cap\n$ and $\dim X(\tau',\tau'')_{0,0} = \dim \overline{\OO}^\lambda\cap\TT_\mu\cap\n$ \acom{why?} irreducible components of $\mathring X(\tau',\tau'')_{0,0}$ are generalized orbital varieties. The isomorphisms of Prop.\ 5 and Lem.\ 8 then give the desired equality (from left to right). 
\end{proof}
% 
\begin{conjecture}
    % Let $Z_i \subset \overline{S^{\nu_i}\cap S^0_-}$ be an MV cycle of weight $\nu_i$ ($i = 1,2$) and put $\nu = \nu_1 + \nu  _2$. 
    Let $\tau$ be the tableau got by taking the union of the rows of $\tau'$ and $\tau''$ and ordering the entries in each row smallest to largest. 
    % Note that $\tau$ has shape $\lambda$, weight $\mu$, and  Lusztig datum equal to the sum of the Lusztig data of $\tau'$ and $\tau''$. 
    Then 
    \begin{equation}
        \iota(Z(\tau), Z(\tau') \circ Z(\tau'')) = 1 \,. 
    \end{equation}
\end{conjecture}
% 
% RESOLVED COMMENTS
% \jcom{Rather than adding the Lusztig data, how can you produce $\tau$ directly from $\tau', \tau''$?  I guess you can just add the GT patterns, so for tableaux you just take the union of the rows, is that right?}
% 
% \acom{Pierre said he hasn't thought about this since he last thought about this and remarked that KKKO would distinguish two terms, a leading and a tailing one.} 
% 
\subsection{Connection to cluster structure on $\CC[N]$}
% 
Goal: 
$$
b_{Z'}b_{Z''} = \sum_{Z\in\cZ(\infty)_{-\nu_1 - \nu_2}} \iota\left(
    Z, Z' \ast_0 Z''
    % \pi^{-1}(0) \cdot \overline{Z_1 \times Z_2 \times U}
\right) b_Z 
$$

\jcom{We should recall the stable MV cycles and the theorem from mvbasis regarding multiplication in $ \CC[N]$.}

>>>>

To prove this we require the following resutl from \cite{dthesis}.
\begin{theorem}
    \label{pr:govsasirrecs}
    The irreducible components of $\overline{\OO}^\lambda\cap\TT_\mu\cap\n$ are $\{{X(\tau)} : \tau\in YT(\lambda)_\mu\}$. 
\end{theorem}
% 
\begin{proof}[Proof of~\Cref{cor:iota}]
Since $\mathring X(\tau',\tau'')_{0,0}\subset\overline{\OO}^\lambda\cap\TT_\mu\cap\n$ and $\dim X(\tau',\tau'')_{0,0} = \dim \overline{\OO}^\lambda\cap\TT_\mu\cap\n$ \acom{why?} irreducible components of $\mathring X(\tau',\tau'')_{0,0}$ are generalized orbital varieties. The isomorphisms of Prop.\ 5 and Lem.\ 8 then give the desired equality (from left to right). 
\end{proof}
% 
\begin{conjecture}
    % Let $Z_i \subset \overline{S^{\nu_i}\cap S^0_-}$ be an MV cycle of weight $\nu_i$ ($i = 1,2$) and put $\nu = \nu_1 + \nu  _2$. 
    Let $\tau$ be the tableau got by taking the union of the rows of $\tau'$ and $\tau''$ and ordering the entries in each row smallest to largest. 
    % Note that $\tau$ has shape $\lambda$, weight $\mu$, and  Lusztig datum equal to the sum of the Lusztig data of $\tau'$ and $\tau''$. 
    Then 
    \begin{equation}
        \iota(Z(\tau), Z(\tau') \circ Z(\tau'')) = 1 \,. 
    \end{equation}
\end{conjecture}
% 
% RESOLVED COMMENTS
% \jcom{Rather than adding the Lusztig data, how can you produce $\tau$ directly from $\tau', \tau''$?  I guess you can just add the GT patterns, so for tableaux you just take the union of the rows, is that right?}
% 
% \acom{Pierre said he hasn't thought about this since he last thought about this and remarked that KKKO would distinguish two terms, a leading and a tailing one.} 
% 
\subsection{Connection to cluster structure on $\CC[N]$}
% 
There is a map from $\irr \overline{\Gr^\lambda\cap S^\mu_-} \to \CC[N]$ that factors through \acom{??} $\overline{S^0_+\cap S^\nu_-}$ for $\nu = \lambda - \mu$. The irreducible components of $ \overline{S^0_+\cap S^\nu_-}$ are called \new{stable MV cycles} and there is a bijection given by multiplication by $t^\lambda$ from $\{Z\in \irr \overline{S^0_+\cap S^\nu_-} : t^\lambda Z \subset\overline\Gr^\lambda\}$ to $\irr \overline{\Gr^\lambda\cap S^\mu_-} $. Moreover, the induced map on $\cup L(\lambda)\to\CC[N]$ is not injective, while that on the collection of all stable MV cycles ($\oplus L(0)_\nu\to\CC[N]$) is.

In \cite{baumann2019mirkovic}, Baumann, Knutson and the third author show that the stable MV cycles define a perfect basis of $\CC[N]$ whose structure constants are given by intersection multiplicities. 
%

\begin{theorem}
    (\cite[Theorem~7.11]{baumann2019mirkovic})
$$
b_{Z'}b_{Z''} = \sum_{Z\in\cZ(\infty)_{-\nu_1 - \nu_2}} \iota\left(
    Z, Z' \ast_0 Z''
    % \pi^{-1}(0) \cdot \overline{Z_1 \times Z_2 \times U}
\right) b_Z 
$$
\end{theorem}

\jcom{We should recall the stable MV cycles and the theorem from mvbasis regarding multiplication in $ \CC[N]$.}
\acom{Begun}
